\begin{problem}{Tree Artisan}{standard input}{standard output}{1 second}{1024 megabytes}

Sejong is a famous tree artisan from Hanyang. Bring him any graph, and he will transform it into a beautiful tree\footnote{A tree is an undirected connected graph with $N$ vertices and $N-1$ edges.}!

You are given a simple graph\footnote{A simple graph is a graph in which every edge connects two distinct vertices, and between any two vertices $u$ and $v$, there is at most one edge.} with $N$ vertices and $M$ edges.

Sejong will add zero or more new edges between vertices $1, 2, \ldots, N$ to turn the graph into a tree.

Before starting his work, Sejong wants to estimate how many ways there are to turn the graph into a tree under the above conditions. Help him determine whether the number of such ways exceeds $K$, and if it does not, find the exact count! Two methods are considered distinct if and only if the sets of added edges differ. All edges are undirected.

\InputFile
The first line contains three integers $N$, $M$, and $K$, separated by spaces. $(2 \le N \le 100\, 000;$ $1 \le M \le 200\, 000;$ $1 \le K \le 3\, 000)$

The next $M$ lines each contain two integers $u_i$ and $v_i$, the endpoints of the $i$-th edge, separated by a space. $(1 \le u_i \lt v_i \le N;$ $(u_i, v_i) \ne (u_j, v_j) )$

\OutputFile
If the number of ways to turn the graph into a tree exceeds $K$, print $-1$. Otherwise, print the exact count.

\Examples

\begin{example}
\exmpfile{example.01}{example.01.a}%
\exmpfile{example.02}{example.02.a}%
\end{example}

\end{problem}

